---
title: "More ggplot2"
author: Reiko Okamoto
date: "`r Sys.Date()`"
format: gfm
editor: visual
---

I can only fit so much into a three-hour workshop! In this document, we'll use the same data set of French train delays to explore additional features of ggplot2.

💻Load the necessary packages:

```{r}
library(tidyverse)
```

💻Read in the data:

```{r}
trains_df <- read_csv("french_trains.csv")
trains_df
```

## 📈Box plots

Box plots are great for visualizing the distribution of a continuous variable across different categories.

💻Create a box plot to show the distribution of average arrival delay across different journeys from "BORDEAUX ST JEAN":

```{r}
trains_df |> 
  filter(departure_station == "BORDEAUX ST JEAN") |> 
  ggplot(aes(x = arrival_station, y = avg_delay_all_arriving)) +
  geom_boxplot()
```

## 📈Violin plots

Violin plots are similar to box plots. However, violin plots reveal the full data distribution, unlike box plots, which only highly summary statistics like the median and interquartile range. This is especially helpful when the data has multiple peaks (i.e., multimodal distribution).

💻Create a violin plot to show the distribution of average arrival delay across different journeys from "BORDEAUX ST JEAN":

```{r}
trains_df |> 
  filter(departure_station == "BORDEAUX ST JEAN") |> 
  ggplot(aes(x = arrival_station, y = avg_delay_all_arriving)) +
  geom_violin()
```

Note that we only had to change one line of code!

## 📈Facet plots

## 📈Modify components of a theme
